Covariates analysis of MSBB RNASeq (with two-step SVA)

### 2016-05-31 code/Rmd/MSSM_RNASeq_SVA_cdr.Rmd
Minor fix

---
title: "Covariates analysis of MSBB RNASeq (with SVA)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)
library(githubr)

@@

@@

## Calculate the number of surrogate variables
NUM.SV = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456)

@@

```{r get.gene.symbols, cache=TRUE, eval=FALSE}
# Define biomart object
mart <- useMart(biomart = "ensembl", dataset = "hsapiens_gene_ensembl", host = )

>>>>

---
title: "Covariates analysis of MSBB RNASeq (with two-step SVA)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)
library(githubr)

@@

source('../R/lib/num.sv')

@@

## Calculate the number of surrogate variables
NUM.SV = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456, LINPACK = TRUE, B = 10)

@@

```{r get.gene.symbols, cache=TRUE, eval=TRUE}
# Define biomart object
mart <- useMart(biomart = "ensembl", dataset = "hsapiens_gene_ensembl", host = )
